\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\title{Movie Review}
\author{Rang De Basanti \& Sholay }
\date{2nd April 2017}
\begin{document}

\maketitle

\section{Rang De Basanti: The story untold}
This story is about six friends who help an English filmmaker create a documentary about Indian freedom struggle. During filming, this group of friends learn about those before them and the importance of fighting for their rights.Every once in a while comes a film that makes you question your indifference towards everything that’s going on around you. That makes you feel almost ashamed for being unconcerned about the state of affairs in your nation. A film that inspires you to wake up and react. To raise your voice, or to put your foot down.

You don’t see such films in India very often. To be honest, you don’t see too many films that stay with you half an hour after you’ve left the movie hall. And that’s why when a film like Rang De Basanti comes along, you stand up and cheer.

Rang De Basanti is the story of a group of young friends in Delhi, who spend the most part of their lives laughing and joking, drinking beer and chilling out.

When they’re urged by a British documentary filmmaker to act in her film about the Indian revolutionaries, their lives change forever.

What they may have until then regarded as outdated, stuffy, text-book values eventually begin to assume greater relevance in their lives.

In the end, the line between past and present blurs as our protagonists become one in spirit with the revolutionaries that they set out portraying. 
\subsection{Cast}

\begin{itemize}
    \item Aamir Khan as Daljit Dj Singh / Chandrashekhar Azad
    \item Siddharth Narayan as Karan Singhania / Bhagat Singh
    \item Atul Kulkarni as Lakshman Pandey / Ramprasad Bismil
    \item Kunal Kapoor as Aslam Khan / Ashfaqullah Khan
    \item Sharman Joshi as Sukhi Ram / Rajguru
    \item Alice Patten as Sue McKinley
    \item Soha Ali Khan as Sonia / Durgawati Devi
    \item R. Madhavan as Flight Lt. Ajay Rathod
\end{itemize}

\section{Sholay}
The moview was awesome. Thakur has no hands :P. In this Indian action/adventure, Thakur (Sanjeev Kumar) has hired two small-time criminals to do some dirty work for him that he cannot get the police to do. He is a retired police inspector and seeks revenge on a bandit and his gang for mutilating him, murdering his family, and terrorizing the poor of his region. Veeru and Jai are agreeable, and soon the gangleader, Gabbar, and his henchmen have reason to regret their previous behavior.
\subsection{Cast}
\begin{itemize}
\item Hema Malini
\item Madhuri Dixit
\item Amitabh Bachchan
\item Dharmendra Singh
\item SRK
  \end{itemize}
\end{document}
